Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-29 bbbq_article.tex
Make graphs more concise, fix #197

\richel{TODO: Tables don't have a legend, but instead have a title and footnotes below the table. Modify the tables to make it so in the end, \url{https://github.com/richelbilderbeek/bbbq_article/issues/181}}

@@

\richel{
  First do the bioinformatics predictions,
  then the experimental confirmation 
}

Figure \ref{fig:1} shows the predicted presentation of TMH-derived peptides in MHC-I,
for a human, viral and bacterial proteome.
Per MHC-I haplotype, it shows the percentage of binders that overlap with a TMH 
for at least one residue.
A dashed line indicates the expected percentage of TMH-derived epitopes 
that would be presented, if TMH-derived epitopes would be presented just as 
likely as soluble regions.
In 12 out of 13 MHC-I haplotypes, TMH-derived epitopes are presented more often 
then the null expectation, for a human proteome. 
For the viral and bacterial proteome, 11 out of 13 haplotypes present
TMH-derived epitopes more often than expected by chance.
The extent of the over-presentation between the various different haplotypes 
is similar for the probed proteomes, which strengthens our previous conclusion (\cite{bianchi2017}) that the hydrophobicity of the MHC-binding groove is the main factor responsible for the predicted over-presentation of TMH-derived peptides.

@@

%\begin{figure}
%  \centering
%  \begin{subfigure}[t]{0.45\textwidth}
%    \centering
%    \caption{}
%    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_f_tmh_mhc1_2_grid.png}
%    \label{fig:1}
%  \end{subfigure}
%  \hfill
%  \begin{subfigure}[t]{0.45\textwidth}
%    \centering
%    \caption{}
%    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_f_tmh_mhc2_2_grid.png}
%    \label{fig:2}
%  \end{subfigure}
%  \caption{
%    TMH-derived peptides are predicted to be over-presented in MHC-I (left
%    panel) and MHC-II (right panel).
%    Both panels show the percentage of epitopes predicted to be 
%    overlapping with TMHs
%    for the proteomes of human, SARS-CoV-2 and \emph{M. tuberculosis}.
%    The dashed horizontal lines indicate the percentage as expected by chance.
%    See supplementary tables \ref{tab:tmh_binders_mhc1} and \ref{tab:tmh_binders_mhc2}
%    for the exact TMH and  epitope counts.
%    \richel{Add panel with hydrophobicity}
%  }
%\end{figure}

@@

We next wondered if the over-representation of TMH-derived peptides would also be present for MHC-II. 
Figure \ref{fig:2} shows the percentages of MHC-II epitopes predicted to be overlapping 
with TMHs for our human, viral and bacterial proteomes.
See supplementary table \ref{tab:tmh_binders_mhc2} 
for the TMH and epitope counts.
We predict that TMH-derived peptides are also over-presented in most MHC-II haplotypes, and this over-presentation seems even more pronounced than for MHC-I. 
\richel{
  Showing how general our finding is (as it is explained by hydrophobicity)
  is important. See \url{https://github.com/richelbilderbeek/bbbq_article/issues/192}
}
Similar to our previous results with MHC-I, we predicted that the extent to which TMH-derived
epitopes are presented by each MHC-II haplotype is similar for the human, bacterial and viral proteome.

@@

Not only do we predict that MHC-I and MHC-II TMH-derived epitopes 
are presented , we conclude that these are additionally
presented more often than expected by chance 
alone (figures \ref{fig:1} and \ref{fig:2}).
This in silico finding is a general pattern 
that persists in both MHC-I and MHC-II, 
for humans, bacteria and viruses.

@@

Tables \ref{tab:tmh_binders_mhc1} and \ref{tab:tmh_binders_mhc2}
show the exact number of binders, binders that overlap with TMHs
and the percentage of binders that overlap with TMHs, as
visualized by figures \ref{fig:1} and \ref{fig:2} respectively.

>>>>

@@

Figure \ref{fig:bbbq_1_smart_results} shows the predicted presentation of TMH-derived peptides in MHC-I,
for a human, viral and bacterial proteome.
Per MHC-I haplotype, it shows the percentage of binders that overlap with a TMH 
for at least one residue.
A dashed line indicates the expected percentage of TMH-derived epitopes 
that would be presented, if TMH-derived epitopes would be presented just as 
likely as soluble regions.
In 12 out of 13 MHC-I haplotypes, TMH-derived epitopes are presented more often 
then the null expectation, for a human proteome. 
For the viral and bacterial proteome, 11 out of 13 haplotypes present
TMH-derived epitopes more often than expected by chance.
The extent of the over-presentation between the various different haplotypes 
is similar for the probed proteomes, which strengthens our previous conclusion (\cite{bianchi2017}) that the hydrophobicity of the MHC-binding groove is the main factor responsible for the predicted over-presentation of TMH-derived peptides.

@@

@@

We next wondered if the over-representation of TMH-derived peptides would also be present for MHC-II. 
Figure \ref{fig:bbbq_1_smart_results} shows the percentages of MHC-II epitopes predicted to be overlapping 
with TMHs for our human, viral and bacterial proteomes.
See supplementary table \ref{tab:tmh_binders_mhc2} 
for the TMH and epitope counts.
We predict that TMH-derived peptides are also over-presented in most MHC-II haplotypes, and this over-presentation seems even more pronounced than for MHC-I. 
\richel{
  Showing how general our finding is (as it is explained by hydrophobicity)
  is important. See \url{https://github.com/richelbilderbeek/bbbq_article/issues/192}
}
Similar to our previous results with MHC-I, we predicted that the extent to which TMH-derived
epitopes are presented by each MHC-II haplotype is similar for the human, bacterial and viral proteome.

@@

Not only do we predict that MHC-I and MHC-II TMH-derived epitopes 
are presented , we conclude that these are additionally
presented more often than expected by chance 
alone (figure \ref{fig:bbbq_1_smart_results}).
This in silico finding is a general pattern 
that persists in both MHC-I and MHC-II, 
for humans, bacteria and viruses.

@@

Tables \ref{tab:tmh_binders_mhc1} and \ref{tab:tmh_binders_mhc2}
show the exact number of binders, binders that overlap with TMHs
and the percentage of binders that overlap with TMHs, as
visualized by figure \ref{fig:bbbq_1_smart_results}.
